\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
AV issue comments inserted in red, #209

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AV edits
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

>>>>

@@

\flag{AV}{Do we say somewhere that once a subject reaches 0.95 it cannot be down
graded even if there are more classifications?}

@@

\flag{AV}{wonder if we should include some definitions for less familiar readers
for false positive: a non-lens that is selected by the crowd,
false negative: a lens candidate that is rejected by the crowd,
true positive: a lens candidate selected by the crowd,
true negative (not used in the paper): an empty field that's correctly
identified as being empty...}
